Learning and comparing functional connectomes across subjects

### 2013-01-01 paper.tex
remove kindle formatting
Progress on abstract

\begin{abstract}
    We are the champion... of the world

>>>>

\begin{abstract}
    Functional connectomes capture brain interactions via 
    fluctuations in brain imaging signal. On rest data they map
    the intrinsic functional architecture of the brain and with
    task-driven experiments they represent the integration mechanisms
    between specialized brain areas. Analysis of their variability 
    across subjects and conditions can reveal markers of brain
    pathologies and cognitive mechanisms. However, connectomes are
    complex multivariate objects. The methodology to estimate them from
    the functional signal, and to compare them is still...
